\subsubsection{Task 2}
\label{ssub:task_2}

\textbf{Change the time slot of an already booked table tennis session (7pm).
Cancel the booking if it is not possible to rearrange}

\textbf{User:} Working
\begin{enumerate}
	\item Press `My Bookings'
	\item Click on the current booking to be rearranged
	\item Press `Change Time'
	\item Browse alternative results
	\item Go Back
	\item Press `Cancel Booking'
	\item Confirm cancellation
\end{enumerate}

\subsubsection{Walkthrough}

\begin{description}
	\item[Choosing new booking] Janet does not initially see an option to amend
		a booking on the homescreen, she does not want to make a new booking so
		she knows she must select `My Details' or `My Bookings'. She is unsure
		but clicks `My Bookings' as it is one of her bookings which she would
		like to change.

	\item[Selecting swimming] Janet is presented with a list of her current and
		past bookings. She clicks the table tennis session at 7pm which then
		shows this booking on a separate screen with a selection of different
		options.

	\item[Selecting disabled access] There is an option `Change Time' which
		Janet clicks. The location of this booking permits customers to change
		booking times, so a search results page is displayed showing available
		booking slots at similar times with all other search criteria remaining
		the same. Unfortunately after browsing through all the results she sees
		there are no available table tennis sessions after 7pm, so Janet must
		cancel.

	\item[Completing the search and choosing the booking] After realising she
		cannot rearrange her booking, Janet returns to the previous page to
		look at other options. She knows she must cancel the session so she
		presses `Cancel Booking' which is clearly visible at the bottom of the
		screen. A prompt is displayed asking her to confirm that she definitely
		wishes to cancel the booking, she is sure so she confirms the
		cancellation. Refunds?
\end{description}

\renewcommand{\arraystretch}{1.3}
\begin{longtabu}{cccccl}
	\toprule
	\textbf{Step} & \textbf{Criteria 1} & \textbf{Criteria 2} &
	\textbf{Criteria 3} & \textbf{Criteria 4} & \textbf{Success?} \\
	\midrule
	1  & y & n & y & n & Success \\
	2  & y & y & y & y & Success \\
	3  & y & y & y & y & Success \\
	4  & y & y & y & y & Success \\
	5  & y & y & y & y & Success \\
	6  & y & y & y & y & Success \\
	7  & y & y & y & y & Success \\
	\bottomrule
\end{longtabu}
