\subsection{Task 3}
\label{ssub:task_3}

\textbf{Weekly tennis sessions with a friend with reminders.}

\textbf{User:} Student
\begin{enumerate}
	\item Select `New Booking'
	\item Press `Sport'
	\item Select `Tennis' and press `Done'
	\item Press `Location'
	\item Press `Find my location'
	\item Slide the distance option down to `within 1km' and press `Done'
	\item Press `Date'
	\item Press `W' to highlight all Wednesdays and press `Done'
	\item Press `Time'
	\item Press `PM' for afternoons and press `Done'
	\item Press `Search'
	\item Press `Price'
	\item Select a listing
	\item Add a number of bookings to the basket
	\item Press `Book now'
	\item Press `Home' in the navigation bar
	\item Press `My bookings'
	\item Select a current booking
	\item Press `Share'
\end{enumerate}

\subsubsection{Walkthrough}

\begin{description}
	\item[Creating a new booking] Jenny immediately presses the `new booking'
		button and selects tennis from the list of sports. She also fills the
		location section with ease. Knowing that both, she and her friend are
		free on Wednesday afternoons, she selects Wednesdays from the calendar.
		Jenny does this by pressing each Wednesday individually as she isn't
		aware that pressing `W' would highlight all Wednesdays this month. She
		presses the PM button on the `Time' page to select afternoons before
		pressing the `Search' button.

	\item[Making multiple bookings] Jenny is aware that multiple bookings could
		cost her a lot and decides to sort the available results by price. She
		selects the cheapest result and sees that multiple bookings are
		available in the `repeated bookings' section. She adds a number of
		these by pressing the basket icon and presses the `Book now' button.

	\item[Sharing booking details with a friend] Once she has made her payment,
		Jenny checks to see if her multiple bookings have been successful. She
		presses the `home' icon in the navigation bar and presses `my bookings'
		from the home-screen. She sees that all of the bookings she made in the
		`current bookings' section.  She selects the first booking for this
		Wednesday, and presses the `share' button to send the details of the
		booking to her friend.
\end{description}

\renewcommand{\arraystretch}{1.3}
\begin{longtabu}{cccccl}
	\toprule
	\textbf{Step} & \textbf{Criteria 1} & \textbf{Criteria 2} &
	\textbf{Criteria 3} & \textbf{Criteria 4} & \textbf{Success?} \\
	\midrule
	1  & y & y & y & y & Success \\
	2  & y & y & y & y & Success \\
	3  & y & y & y & y & Success \\
	4  & y & y & y & y & Success \\
	5  & y & y & y & y & Success \\
	6  & y & y & y & y & Success \\
	7  & y & y & y & y & Success \\
	8  & y & n & n & y & Success \\
	9  & y & y & y & y & Success \\
	10 & y & y & y & y & Success \\
	11 & y & y & y & y & Success \\
	12 & y & y & y & y & Success \\
	13 & y & y & y & y & Success \\
	14 & y & y & y & y & Success \\
	15 & y & y & y & y & Success \\
	16 & y & y & y & y & Success \\
	17 & y & y & y & y & Success \\
	18 & y & y & y & y & Success \\
	19 & y & y & y & y & Success \\
	\bottomrule
\end{longtabu}

\begin{description}
	\item[Additional Notes] Although the user was able to achieve the steps, it
		isn't possible for Jenny to set up weekly reminders for her friend, she
		must either share the bookings with her each week, or remind them
		herself.

		It also isn't possible for Jenny to share the details of available
		bookings with her friend before making a booking, which could result in
		having to make multiple cancellations or rearrangements if the date or
		time becomes unsuitable for her friend.

\end{description}
