\renewcommand{\arraystretch}{2}
\begin{longtabu}{p{0.3\linewidth} c X}
	\toprule
	\textbf{Scenario} & \textbf{Rating} & \textbf{Comment}\\
	\midrule
	\multicolumn{3}{l}{\textbf{Elderly}}\\
	\midrule
	Searching for new sports in the area and notifying his wife of the booking.
	& $+$ & If Howards wishes to search only by location he has the option to
	leave the sports criteria blank or `select all' sports. Under the location
	criteria he can then either enter a postcode or use GPS and specify the
	maximum amount of kilometres he is willing to travel. Once the results are
	displayed he can sort them by distance to see which sports are available
	nearest to him. If Howard prefers a visual representation of what sports
	are available locally, he can press the map button. He can also send the
	details of his bookings to his wife by using the `share' button. \\

	Racquet sport with 4 friends on Friday & 0 & Using the `All Sports' tab,
	Howard can select racquet sports. There is no option to specify how many
	players, or how many courts he would like to book. Under the date criteria,
	he can select `F' which will highlight all Fridays. After Howard clicks on
	his chosen booking, the following screen displays his booking along with
	`Repeated bookings' which he can also add to his basket. \\

	Swimming nearby with knee pain & + & Howard can specify swimming as his
	chosen sport and use his current location courtesy of GPS\@. He may choose
	to set the maximum distance he is willing to travel so he does not see
	results too far for him to physically travel. Or he can filter the results
	by distance and simply look at the first few options. If Howard's knee pain
	is particularly bad he may wish to swim somewhere which doesn't require
	climbing any stairs. He can do this by ticking the `disabled access' option
	under location. \\

	\multicolumn{3}{l}{\textbf{Working}}\\
	\midrule
	Team sport on Friday including screen sharing with friends & 0 & Janet can
	select the Team option from the drop down menu in the sports criteria
	section. She may wish to group the sports when looking at the results for
	better clarity. Screen sharing is not available but she can send the
	booking details to her friends using the `share' option. \\

	Change/cancel booking at late notice & + & By going into `My Bookings'
	Janet can choose `Change time'. If she is unable to rearrange she can also
	cancel the booking. Whether she is eligible for a refund depends on the
	sports centre's policy. \\

	Outdoor sport early on Saturday & $+$ & Similar to the team sports
	scenario, Janet can choose to see only outdoor sports. Under the time
	criteria, she can select the `AM' button which will select all times
	between 12am and 11am. The weather prediction may also influence her
	decision of when to play. \\

	\multicolumn{3}{l}{\textbf{Student}}\\
	\midrule
	Tennis court at specific times & $+$ & Jenny can specify tennis as the
	sport she would like to play. She can also select a variety of specific
	time slots on the time criteria page. \\

	Weekday evening session must be on clay & 0 & Jenny can choose not to
	select a date and click `PM' under the time criteria to see only evening
	sessions. She would have to contact the sports centre to find out the
	surface of the tennis court. \\

	Weekly practice with friend with reminders & 0 & Jenny can book weekly
	sessions using the `Repeated bookings' option. She can share the booking
	information with her friend using the `share' icon button, however there is
	no notification feature. \\

	\multicolumn{3}{l}{\textbf{Child}}\\
	\midrule
	Outdoor sport close to home or on a bus route with coach & 0 & Just like
	Janet, Joe can select the outdoor option to display a variety of outdoor
	sports. He can specify a maximum distance from home or sort the results by
	distance to find venues close to him. Under the location criteria, he can
	choose to display results where the venue is reachable using public
	transport within a certain time. This feature does not specify what form of
	transport would take him to the venue. Joe would have to perform two
	separate searches for venues within walkable distance and those offering
	public transport. \\

	Booking several squash courts for after school tournament & $-$ & There is
	no feature to choose how many courts are required. Joe would have to add
	the booking to his basket, search again, then add another booking several
	times. There is also no option for Joe to specify the duration, which could
	be important if the tournament was predicted to last several hours. \\

	Looking for high quality tennis court & $-$ & There is no way of accessing
	user reviews and ratings of the sport venues. Nor is there an indication of
	the quality of any of the facilities. \\
	\bottomrule
\end{longtabu}
