\renewcommand{\arraystretch}{2}
\begin{longtabu}{p{0.3\linewidth} c X}
	\toprule
	\textbf{Criteria} & \textbf{Rating} & \textbf{Comment}\\
	\midrule
	Visibility of system status & $+$ & Clear headings show where in the
	booking process the user is. A simple structure to the pages means that
	returning to the home screen is easy and allows the user to view prior
	bookings.\\

	Match between system and the real world & 0 & Simple, clear, short
	instructions and pieces of information are used to minimise the reading
	onscreen, whilst making the purpose of each selection object clear. The
	sports selection drop down menu is not immediately self explanatory.\\

	User control and freedom & 0 & All stages of the booking allow the user to
	move backwards to a previous state. Since the final booking is handled by
	the independant sports centers, it is up to them to implement some
	verification with the user that the booking details are correct.\\

	Consistency and standards & $+$ & Well recognised icons are used throughout
	which correspond to the same functionality in other applications. \\

	Error prevention & 0 & The settings for the search criteria can all be
	changed before finally selecting `search'. It is not obvious that the time
	of a booking can be changed easily from the bookings screen, and the other
	details of the booking cannot be changed. To do this, the user has to enter
	a new set of search criteria.\\

	Recognition rather than recall & 0 & All icons are chosen to represent the
	function to which they apply to reduce recall. \\

	Flexibility and efficiency of use & $-$ & The user can make repeated
	bookings of for similar searches, but bulk bookings where more than the
	date changes are not possible. \\

	Aesthetic and minimalist design & $+$ & The design is clean and simple with
	bold colours to differentiate sections, headers and icons. There are a lot
	of different icons on the results pages which could make them look
	confusing when the user is not familiar with the structure and layout of
	the page.\\

	Help users recognize, diagnose, and recover from errors & $-$ & There is no
	undo button or selection to revert back to a previous state, the user must
	instead select a new set of search criteria.\\

	Help and documentation & 0 & There is a help button to display information
	about the features availible on the current screen.\\
	\bottomrule
\end{longtabu}
