\section{Methods of Evaluation}
\label{sec:methods_of_evaluation}

The design process is aided by the generation and evaluation of a number of
first and second generation prototypes. These will be assessed against several
specific criteria as well as the user personas defined in Section~%
\ref{sec:user_personas}. Using the results from these evaluations, the
best aspects of the first prototypes will be used to inform the second
generation.

When evaluating the initial designs, each of the potential scenarios are
examined and the prototype tested to see if it provides the required or desired
functionality. Where the functionality is not provided by a prototype, the
impact of the implementation of that feature on the rest of the design will be
analysed to see if it is possible to add this feature.

In addition to these real world situations, the designs are tested against a
set of heuristics called Neilsen's heuristics\cite{nielsonheuristics} which
allow individual elements of the user interface design to be evaluated in
isolation against recognised principles. A description of each of the
heuristics that are considered is given below.

\begin{description}

	\item[Visibility of system status]\hfill \\ The activity that is currently
		being performed should be clear to the user, and the status of that
		activity should be clear. For example, if a process is running,
		waiting, or completed.

	\item[Match between system and the real world]\hfill \\ Using standard
		conventions for ordering items makes them easier to search through and
		select. Also the wording of buttons, labels and information should be
		familiar to the user. However, the computer system should not try to
		imitate a physical object directly, i.e.\ skeuomorphism.

	\item[User control and freedom]\hfill \\ The user should be in control of
		the system. The system should work for them, but provide the ability to
		undo mistaken actions.

	\item[Consistency and standards]\hfill \\ Any methods for interacting with
		the system should be uniform across different platforms so that users
		do not need to relearn to use the system.

	\item[Error prevention]\hfill \\ Reducing the possibility of errors, and
		the ability for the user to provide data that could cause an error is
		better than recovering from errors. If an error does happen, then
		giving the user information is generally better than leaving them
		without knowing what happened.

	\item[Recognition rather than recall]\hfill \\ Having navigational elements
		clearly visible and reachable means that the user does not need to
		remember how to use the application, instead the instructions are
		effectively on-screen.

	\item[Flexibility and efficiency of use]\hfill \\ Catering to advanced
		users without distracting or confusing the novice allows the system to
		be used by a wider range of people.

	\item[Aesthetic and minimalist design]\hfill \\ Including irrelevant data,
		or information that is only needed infrequently can be distracting.
		Reducing the number of visual stimuli presented to the user can
		increase speed and efficiency.

	\item[Help users recognize, diagnose, and recover from errors]\hfill \\
		Easy to read, simple error messages, briefly explaining what happened
		can help the user to not get into the same situation again.

	\item[Help and documentation]\hfill \\ Providing documentation in a well
		structured way can help the tentative user to use the basic
		functionality and the advanced user find more.

\end{description}
