\section{Recommendations}
\label{sec:recommendations}

To take this design forward we would require further prototyping to implement
the changes suggested in Section~\ref{sec:summary}.  There are a number of
additional features that we would add and several changes we would make. The
main aspects we would focus on are:

\begin{itemize}
	\item Ratings system for each location.
	\item Easier search options for booking multiple courts at once.
	\item Search options for length of booking.
	\item Notifications/reminders.
	\item Simplified sorting and grouping options.
	\item Improved error prevention.
\end{itemize}

As some of these changes are brand new features, it would be important to
prototype them before implementing them in the final design so that we could
evaluate whether they actually work in the way a user would want and expect
them to.

In addition to changing the mobile design, it could be possible to design a
similar system for the web so that users can make bookings online on a desktop
computer or laptop. This could be particularly useful for an elderly or
physically impaired user who finds a mobile phone difficult to use or a user
without a smartphone. However, this was beyond the scope of this project.

If we were to actually implement the mobile design, there are feasibility
problems which we would need to overcome. We would need to get the data for the
available sports at each location and the data for the individual booking slots
at each location and whether the booking slots were already booked or not. This
would be possible through two methods:

\begin{enumerate}
	\item Direct involvement of the sports facilities. They would provide the
		data directly to us and would allow a connection to their own systems
		in order to actually make, cancel and change the bookings.

	\item Scraping the data from the websites of each facilities, or get access
		to the data through APIs provided by these websites. In order to make a
		booking, the user would be redirected to the website of that particular
		facility.
\end{enumerate}

The first option is preferable as it would allow the user to make and amend
bookings directly through the application. The prototypes that we have made in
this project would require the involvement of the sports facilities. If, going
forward, this were to be revealed as unfeasible, we could possibly use the
second method above. This would require a lot of changes in the design and
therefore numerous more prototypes.
